Complex Geometry - Index of Notations and ideas

### 2016-08-18 Complex Geometry - index/Complex Geometry - index.tex
Daily update. Complex Geometry notes.

@@

    \textcolor{blue}{$P^k$} $\subset\bigwedge^kV^*$: is the subspace
    of all primitive elements.
    (\textbf{pp.36})
\section{2.Complex Manifolds}

@@

    \begin{figure}[H]
        \centering
        \includegraphics[width=1.3\linewidth]{pics/{prop-1.2.30-pp.36}.pdf}
        \caption{Morphisms}
    \end{figure}
\end{prop}
(\textbf{pp.36 of \cite{book}})
\begin{thebibliography}{1}
	\bibitem{book} Complex Geometry
\end{thebibliography}
\part{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
\end{document}

>>>>

% To include PDF in higher version format.
\pdfoptionpdfminorversion=6

@@

    \textcolor{blue}{$P^k$} $\subset\bigwedge^kV^*$: is the subspace
    of all primitive elements.
    (\textbf{pp.36})

    \textcolor{blue}{Hodge-Riemann pairing $Q$}:
    $$\bigwedge^kV^*\times\bigwedge^kV^*\to \mathbb{R}\text{, }
     (\alpha,\beta)\mapsto (-1)^{k(k-1)}{2}\alpha\wedge\beta\wedge w^{n-k}$$

    Note: here we identify $\bigwedge^{2n}V^*$ with $\mathbb{R}$ 
    by the volumn form $\text{vol}$. Also the $\mathbb{C}$-linear 
    extension of this is still denoted $Q$.

\section{2.Complex Manifolds}

@@

    \begin{figure}[H]
        \centering
        \includegraphics[width=0.9\linewidth]{pics/{prop-1.2.30-pp.36}.pdf}
        \caption{Morphisms}
    \end{figure}
\end{prop}
(\textbf{pp.36 of \cite{book}})

As shown in the theorem, the map $\Lambda^{n-k}$ is produce a mirror
effect in $\bigwedge^*V^*$, very similar to the Hodge $*$.
The next proposition relates the two:

\begin{prop}
    For all $\alpha\in P^k$, we have:
    \begin{align}
        *L^j \alpha = (-1)^{\frac{k(k+2)}{2}}
            \frac{j!}{(n-k-j)!}\cdot L^{n-k-j}I(\alpha).
    \end{align}
\end{prop}
Particularly, when $j=k=0$, we have $*1=\text{vol} = \frac{\omega^n}{n!}$,
or,
\begin{align}
    n!\text{vol} = \omega^n
\end{align}
(\textbf{pp.37 of \cite{book}})

\begin{coro}[Hodge—Riemann bilinear relation]
    \begin{align}
        Q(\bigwedge^{p,q}V^*, \bigwedge^{p',q'}V^*)=0
    \end{align}
    for $(p,q)\neq (p',q')$, and
    \begin{align}
        i^{p-q}Q(\alpha,\bar\alpha)=(n-(p+q))! \cdot
        \langle\alpha,\alpha\rangle_{\mathbb{C}}>0
    \end{align}
    for $0\neq\alpha\in P^{p,q}$, with $p+q\leq n$.
\end{coro}
(\textbf{pp.39 of \cite{book}})
\begin{thebibliography}{1}
	\bibitem{book} Complex Geometry
\end{thebibliography}
\part{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
\end{document}
